% Template for post or presentation abstracts submitted to ILAS 2022
% 1. Fill in the presenter's information (name, affiliation, email
% address) and talk information (title of presentation, abstract).
% 2. Compile to make sure there are no errors.
% 3. Save the .tex file for your abstract with a distinctive name,
% ideally "FamilynameGivenname.tex".
% 4. Upload your .tex file to https://clr.ie/129557
%       
% * Please keep your LaTeX commands simple, and avoid the use of
%    user-defined macros.
% * Include details of co-authors and funding acknowledgements after the abstract.
% * Upload only the LaTeX file (with .tex extension).
% * Questions: Contact Niall Madden (Niall.Madden@NUIGalway.ie)

\documentclass[a4paper]{amsart} 
\usepackage{amssymb} 
\usepackage{hyperref}
\pagestyle{empty}
\date{} 

%% IGNORE THE NEXT 4 LINES
\makeatletter % 
\def\labelenumi{\theenumi.}
\def\theenumi{\@arabic\c@enumi}
\makeatother
%% STOP IGNORING NOW

\begin{document}

\title{Preconditioned iterative methods for multiple saddle-point systems arising from PDE-constrained optimization}
\author{John W. Pearson} %Presenting author only
\address{University of Edinburgh} % Affiliation of presenting author
\email{j.pearson@ed.ac.uk} % Email address of presenting author only

\maketitle

% The abstract  ***no more than one page***

Optimization problems subject to PDE constraints form a mathematical tool that can be applied to a wide range of scientific processes, including fluid flow control, medical imaging, biological and chemical processes, and many others. These problems involve minimizing some function arising from a physical objective, while obeying a system of PDEs which describe the process. Of key interest is the numerical solution of the discretized linear systems arising from such problems, and in this talk we focus on preconditioned iterative methods for these systems.

In particular, we describe recent advances in the preconditioning of multiple saddle-point systems, specifically positive definite preconditioners which can be applied within MINRES, which may find considerable utility for solving these optimization problems as well as other applications. We discuss an inexact active-set method for large-scale nonlinear PDE-constrained optimization problems, coupled with block diagonal and block triangular preconditioners for multiple saddle-point systems which utilize suitable approximations for the relevant Schur complements.

Further, we discuss an alternative structure of a preconditioner for multiple saddle-point systems, which may be applied within the MINRES algorithm and lead to a guaranteed convergence rate, and often demonstrates superior convergence as opposed to widely-used block diagonal preconditioners.

%% Coauthor details here (optional - delete if not applicable)
% and funding acknowledgment (optional - delete if not applicable)
\emph{This is joint work with Andreas Potschka (TU Clausthal), with associated papers available at \cite{PP1,PP2}.}

\begin{thebibliography}{1}

\bibitem{PP1}
John W. Pearson and Andreas Potschka.
\newblock A Preconditioned Inexact Active-Set Method for Large-Scale Nonlinear Optimal Control Problems.
\newblock arXiv preprint \texttt{arXiv:2112.05020}, 2021.

\bibitem{PP2}
John W. Pearson and Andreas Potschka.
\newblock On Symmetric Positive Definite Preconditioners for Multiple Saddle-Point Systems.
\newblock arXiv preprint \texttt{arXiv:2106.12433}, 2022.

\end{thebibliography}


\end{document}


% Please leave the next bit alone  
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ILAS-2022"
%%% End:
