% Template for post or presentation abstracts submitted to ILAS 2022
% 1. Fill in the presenter's information (name, affiliation, email
% address) and talk information (title of presentation, abstract).
% 2. Compile to make sure there are no errors.
% 3. Save the .tex file for your abstract with a distinctive name,
% ideally "FamilynameGivenname.tex".
% 4. Upload your .tex file to https://clr.ie/129557
%       
% * Please keep your LaTeX commands simple, and avoid the use of
%    user-defined macros.
% * Include details of co-authors and funding acknowledgements after the abstract.
% * Upload only the LaTeX file (with .tex extension).
% * Questions: Contact Niall Madden (Niall.Madden@NUIGalway.ie)

\documentclass[a4paper]{amsart} 
\usepackage{amssymb} 
\usepackage{hyperref}
\pagestyle{empty}
\date{} 

%% IGNORE THE NEXT 4 LINES
\makeatletter % 
\def\labelenumi{\theenumi.}
\def\theenumi{\@arabic\c@enumi}
\makeatother
%% STOP IGNORING NOW

\begin{document}

\title{Richard, Matrices and Polyhedra}
\author{Geir Dahl} %Presenting author only
\address{University of Oslo} % Affiliation of presenting author
\email{geird@math.uio.no} % Email address of presenting author only

\maketitle

% The abstract  ***no more than one page***

It is a pleasure to participate in this session where we honor  the work of Richard (A. Brualdi). Richard is, and has been, a central person in our community, and his research in combinatorics and matrix theory is highly acknowledged. 
Personally I have had the pleasure of knowing and collaborating with Richard for more than 20 years. In this talk I will briefly mention a few topics that have been central in Richard's research, and how they might be connected. The talk will be informal, non-technical and focus on Richard and his mathematics, and our collaboration.


%% Coauthor details here (optional - delete if not applicable)
% and funding acknowledgment (optional - delete if not applicable)


\begin{thebibliography}{1}

 \bibitem{RAB-Ryser} R.A.~Brualdi, H.J. Ryser, {\it Combinatorial Matrix Theory}, Cambridge University Press, 1991.

 \bibitem{RAB} R.A.~Brualdi, {\it Combinatorial Matrix Classes}, Cambridge University Press, 2006.


 \bibitem{BD1} R.A.~Brualdi,  G.~Dahl, Alternating sign matrices, extensions and related cones, {\it Adv. in  Appl. Math.}, 86 (2017), 19--49.
 
 
\end{thebibliography}


\end{document}


% Please leave the next bit alone  
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ILAS-2022"
%%% End:
