% Template for post or presentation abstracts submitted to ILAS 2022
% 1. Fill in the presenter's information (name, affiliation, email
% address) and talk information (title of presentation, abstract).
% 2. Compile to make sure there are no errors.
% 3. Save the .tex file for your abstract with a distinctive name,
% ideally "FamilynameGivenname.tex".
% 4. Upload your .tex file to https://clr.ie/129557
%       
% * Please keep your LaTeX commands simple, and avoid the use of
%    user-defined macros.
% * Include details of co-authors and funding acknowledgements after the abstract.
% * Upload only the LaTeX file (with .tex extension).
% * Questions: Contact Niall Madden (Niall.Madden@NUIGalway.ie)

\documentclass[a4paper]{amsart} 
\usepackage{amssymb} 
\usepackage{hyperref}
\pagestyle{empty}
\date{} 

%% IGNORE THE NEXT 4 LINES
\makeatletter % 
\def\labelenumi{\theenumi.}
\def\theenumi{\@arabic\c@enumi}
\makeatother
%% STOP IGNORING NOW

\begin{document}

\title{Assigned rational functions of a rooted tree}
\author{Ivan Damnjanovi\'c} %Presenting author only
\address{Diffine LLC \& Faculty of Electronic Engineering, University of Ni\v{s}}
\email{ivan.damnjanovic@elfak.ni.ac.rs} % Email address of presenting author only

\maketitle

% The abstract  ***no more than one page***

We investigate the spectral properties of rooted trees with the intention of improving the currently existing results that deal with this matter. The concept of an assigned rational function is recursively defined for each vertex of a rooted tree. Afterwards, two mathematical formulas are given which show how the characteristic polynomials of the adjacency and Laplacian matrix can be represented as products of the aforementioned rational functions. In order to demonstrate their general use case scenario, the obtained formulas are subsequently implemented on balanced trees, with a special focus on the Bethe trees. In the end, some of the previously derived results are used in order to construct a tree merging procedure which preserves the spectra of all of the starting trees.

%% Coauthor details here (optional - delete if not applicable)
% and funding acknowledgment (optional - delete if not applicable)
\emph{Supported by Diffine LLC.}

\begin{thebibliography}{1}

\bibitem{igd_gutman_energy}
{\sc I. Gutman:}
{\it The energy of a graph.}
Ber.\ Math.-Statist.\ Sekt.\ Forsch.\ Graz, 103 (1978), 1--22

\bibitem{igd_heilmann_lieb}
{\sc O.J. Heilmann, E.H. Lieb:}
{\it Theory of monomer-dimer systems.}
Comm.\ Math.\ Phys., 25 (1972), 190--232

\bibitem{igd_rojo_1}
{\sc O. Rojo, R. Soto:}
{\it The spectra of the adjacency matrix and Laplacian matrix for some balanced trees.} Linear Algebra and its Applications, 403 (2005), 97--117

\bibitem{igd_rojo_2}
{\sc O. Rojo, M. Robbiano:}
{\it An explicit formula for eigenvalues of Bethe trees and upper bounds on the largest eigenvalue of any tree.}
Linear Algebra and its Applications, 427 (2007), 138--150

\bibitem{igd_heydari}
{\sc A. Heydari, B. Taeri:}
{\it On the characteristic polynomial of a special class of graphs and spectra of balanced trees.}
Linear Algebra and its Applications, 429 (2008), 1744--1757

\bibitem{igd_bokhary_energy}
{\sc S.A.u.H. Bokhary, H. Tabassum:}
{\it The energy of some tree dendrimers.}
J.\ Appl.\ Math.\ Comput., doi: 10.1007/s12190-021-01531-y (2021)

\bibitem{igd_dickson_polynomials}
{\sc R. Lidl, G.L. Mullen, G. Turnwald:}
{\it Dickson polynomials.}
pp.\ 9--10. Longman Scientific \& Technical, Harlow; copublished in the United States with John Wiley \& Sons, Inc., New York (1993)

\bibitem{igd_spectra_of_graphs}
{\sc A.E. Brouwer, W.H. Haemers:}
{\it Spectra of Graphs.}
pp.\ 18--18. Springer-Verlag New York, New York (2012)

\bibitem{igd_szego}
{\sc G. Szeg\"{o}:}
{\it Orthogonal Polynomials.}
pp.\ 105--106. American Mathematical Society, Rhode Island (1939)

\end{thebibliography}
\end{document}


% Please leave the next bit alone  
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ILAS-2022"
%%% End: