\documentclass{layers17}
\begin{document}


%Please ignore this line:
\FLD{1}{3}{00}{28}{04}{0}
%\runningheads{J.\ Someone and P. \ Someonelse} {Title}

\title{Fitting fitted meshes for a meshless method }
\author{\underline{Place H\"older$^*$} and Co. Author$^{\dagger}$}
\def\PresentingAuthor{P.\ H\"older}

%% DO NOT CHANGE THE NEXT TWO LINES
%\addcontentsline{toc}{section}{\textbf{\PresentingAuthor}
%  \textnormal{\thetitle} \dotfill} 
%% OK - you can start editing again

\address{$^*$\
School of Mathematical Sciences,
Dublin City University.\\
E-mail: \texttt{Your.Name@DCU.ie}
\
%web page: \texttt{http://www.where.ever/}
\\
$^{\dagger}$School of Mathematics, Statistics, and Applied Mathematics, 
NUI Galway.\\
E-mail: \texttt{Co.Author@NUIGalway.ie}
}

%\footnotetext[5]{This work was supported by ...}



\received{} \revised{} \noaccepted{}


%--------------------------------------------------------------------------
%
The length of the following short abstract might vary from 1 to a few paragraphs.
%--------------------------------------------------------------------------

\begin{shortabstract}


Interior layers can appear in linear singularly perturbed parabolic problems when the data


\end{shortabstract}



\keywords{time dependent, interior layers.}

%\ams{65L70, 65L50, 65L10, 65L12.}


%--------------------------------------------------------------------------

% The rest of this sample file is optional (except for the final line).

% It is up to you whether to include more material and/or references or not.
%--------------------------------------------------------------------------


\begin{thebibliography}{9}



\bibitem{bulg-interior} R. K. Dunne and E. O' Riordan, Interior layers arising in linear singularly  perturbed differential equations with discontinuous coefficients,  Proceedings of the Fourth International Conference on Finite Difference Methods: Theory and Applications, Lozenetz, Bulgaria, August 26--29, 2006 (I. Farago, P. Vabishchevich and L.Vulkov eds.), Rousse University, Bulgaria, 2007,  29--38. (extended version appeared as DCU preprint 2006, MS-06-09).


\bibitem{hemker} P. W. Hemker and G.I. Shishkin,
Approximation of parabolic PDEs with a discontinuous initial condition,
{\em East-West J. Numer. Math}, {\bf 1}(4), 287--302, 1993.



\bibitem{perth} E. O' Riordan and G. I. Shishkin Singularly perturbed
parabolic problems with non-smooth data,  {\em Journal Computational and Applied Mathematics}, 2004, v. 166, n. 1, 233-245.


\end{thebibliography}


%--------------------------------------------------------------------------



\end{document}
