% Template for post or presentation abstracts submitted to ILAS 2022
% 1. Fill in the presenter's information (name, affiliation, email
% address) and talk information (title of presentation, abstract).
% 2. Compile to make sure there are no errors.
% 3. Save the .tex file for your abstract with a distinctive name,
% ideally "FamilynameGivenname.tex".
% 4. Upload your .tex file to https://clr.ie/129557
%       
% * Please keep your LaTeX commands simple, and avoid the use of
%    user-defined macros.
% * Include details of co-authors and funding acknowledgements after the abstract.
% * Upload only the LaTeX file (with .tex extension).
% * Questions: Contact Niall Madden (Niall.Madden@NUIGalway.ie)

\documentclass[a4paper]{amsart} 
\usepackage{amssymb} 
\usepackage{hyperref}
\pagestyle{empty}
\date{June 2022} 

%% IGNORE THE NEXT 4 LINES
\makeatletter % 
\def\labelenumi{\theenumi.}
\def\theenumi{\@arabic\c@enumi}
\makeatother
%% STOP IGNORING NOW
\newcommand{\RMC}{R.~M.~Corless}

\begin{document}

\title{Algebraic Companions}
\author{Robert M.~Corless} %Presenting author only
\address{University of Western Ontario} % Affiliation of presenting author
\email{rcorless@uwo.ca} % Email address of presenting author only

\maketitle

% The abstract  ***no more than one page***
Given companion matrix pencils for polynomials $a(x)$ and $b(x)$, and generalized standard triples for them, one can construct a new companion pencil for $c(x) = xa(x)b(x)+d$ using the smaller pencils as building blocks.  Similarly, algebraic linearizations can be built out of smaller linearizations for matrix polynomials.

Working backwards from $c(x)$ is harder, but may be of interest in a search for greater numerical stability.  We already know of recursive constructions for the companions for the Mandelbrot polynomial where the eigenvalue condition number is \textsl{exponentially} smaller than that of the Frobenius companion matrix.  Are there other examples where this approach can be so successful?  And what role does ``minimal height'' play, here?

%% Coauthor details here (optional - delete if not applicable)
% and funding acknowledgment (optional - delete if not applicable)
\textsl{I gratefully acknowledge the help of Eunice Y.S. Chan, Piers W.~Lawrence, and Steven E.~Thornton.  Discussions with Neil J.~Calkin, Laureano Gonzalez-Vega, Nick Higham, J.~Rafael Sendra, and Juana Sendra were also very useful.  Partially supported by NSERC grant RGPIN-2020-06438, and
partially supported by the grant PID2020-113192GB-I00 (Mathematical Visualization: Foundations, Algorithms and Applications) from the Spanish MICINN. }

\begin{thebibliography}{1}
\bibitem{new}Eunice Y.S. Chan and \RMC,  \href{https://journals.uwyo.edu/index.php/ela/article/view/1781}{A new kind of companion matrix} The Electronic Journal of Linear Algebra,  32 pp 335--342 (2017)
\bibitem{minimal}E.Y.S. Chan and \RMC, \href{https://link.springer.com/article/10.1007/s11786-018-0364-2}{Minimal Height Companion Matrices for Euclid Polynomials} Math. in Comp Sci 13 pp 1-16 (2018).
\bibitem{alglin}Eunice Y.S. Chan, \RMC,  L. Gonzalez-Vega, J. Rafael Sendra and Juana Sendra, \href{ https://doi.org/10.1016/j.laa.2018.10.028}{Algebraic
Linearizations of Matrix Polynomials}, Lin. Alg. Appl., 563: 373-399, (2019)
\bibitem{Mandelbrot} Neil J.~Calkin, Eunice Y.~S.~Chan, and \RMC, ``Some facts and conjectures about Mandelbrot polynomials'', \href{https://doi.org/10.5206/mt.v1i1.14037}{Maple Transactions 1, 1, 14037} July 2021.
\bibitem{triples}
Eunice Y.S.~Chan, \RMC, and Leili Rafiee Sevyeri, ``Generalized Standard Triples'', \href{https://doi.org/10.13001/ela.2021.4975}{Electronic Journal of Linear Algebra} Vol 37. September (2021) pp 640--658.
\bibitem{fractal} Neil J.~Calkin, Eunice Y.S.~Chan, \RMC,  David J.~Jeffrey, and Piers W.~Lawrence, “A Fractal Eigenvector”.  Accepted 2021.03.25 to the American Mathematical Monthly. \href{https://arxiv.org/abs/2104.01116}{arXiv preprint}
\end{thebibliography}


\end{document}


% Please leave the next bit alone  
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ILAS-2022"
%%% End:
