% Template for post or presentation abstracts submitted to ILAS 2022
% 1. Fill in the presenter's information (name, affiliation, email
% address) and talk information (title of presentation, abstract).
% 2. Compile to make sure there are no errors.
% 3. Save the .tex file for your abstract with a distinctive name,
% ideally "FamilynameGivenname.tex".
% 4. Upload your .tex file to https://clr.ie/129557
%       
% * Please keep your LaTeX commands simple, and avoid the use of
%    user-defined macros.
% * Include details of co-authors and funding acknowledgements after the abstract.
% * Upload only the LaTeX file (with .tex extension).
% * Questions: Contact Niall Madden (Niall.Madden@NUIGalway.ie)

\documentclass[a4paper]{amsart} 
\usepackage{amssymb} 
\usepackage{hyperref}
\pagestyle{empty}
\date{} 

%% IGNORE THE NEXT 4 LINES
\makeatletter % 
\def\labelenumi{\theenumi.}
\def\theenumi{\@arabic\c@enumi}
\makeatother
%% STOP IGNORING NOW

\begin{document}

\title{Combinatorial Perron Parameters and Classes of Trees}
\author{Enide Andrade} %Presenting author only
\address{Department of Mathematics, University of Aveiro, Portugal} % Affiliation of presenting author
\email{enide@ua.pt} % Email address of presenting author only

\maketitle

% The abstract  ***no more than one page***
%%%%%%%%%%%%%%%%%%%%%

The main goal of this talk is to present recent results related with the combinatorial Perron parameters 
introduced in [1,2] for certain classes of trees, and related bounds for these parameters. These parameters are related to algebraic connectivity of trees and corresponding centers.\\


%%%%%%%%%%%%%%%%%%%%

%% Coauthor details here (optional - delete if not applicable)
% and funding acknowledgment (optional - delete if not applicable)
\emph{This is joint work with Lorenzo Ciardo (University of Oxford) and Geir Dahl (University of Oslo).}\\
\emph{Enide Andrade is supported by Center for Research and Development 
in Mathematics and Applications (CIDMA) through the Portuguese 
Foundation for Science and Technology 
(FCT - Funda\c c\~ao para a Ci\^{e}ncia e a Tecnologia), 
UIDB/04106/2020 and UIDP/04106/2020.}\\

\begin{thebibliography}{9}

\item E. Andrade, G. Dahl.
\newblock Combinatorial Perron Values of Trees and Bottleneck Matrices.
\newblock {\em  Linear and Multilinear Algebra}  65: 2387--2405,  (2017).

\item
 E. Andrade, L. Ciardo, G. Dahl.
 \newblock Combinatorial Perron Parameters for
Trees.
\newblock {\em  Linear Algebra Appl.} 566: 138--166, (2019).


\end{thebibliography}


\end{document}


% Please leave the next bit alone  
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ILAS-2022"
%%% End:
