% Template for post or presentation abstracts submitted to ILAS 2022
% 1. Fill in the presenter's information (name, affiliation, email
% address) and talk information (title of presentation, abstract).
% 2. Compile to make sure there are no errors.
% 3. Save the .tex file for your abstract with a distinctive name,
% ideally "FamilynameGivenname.tex".
% 4. Upload your .tex file to https://clr.ie/129557
%       
% * Please keep your LaTeX commands simple, and avoid the use of
%    user-defined macros.
% * Include details of co-authors and funding acknowledgements after the abstract.
% * Upload only the LaTeX file (with .tex extension).
% * Questions: Contact Niall Madden (Niall.Madden@NUIGalway.ie)

\documentclass[a4paper]{amsart} 
\usepackage{amssymb} 
\usepackage{hyperref}
\pagestyle{empty}
\date{} 

%% IGNORE THE NEXT 4 LINES
\makeatletter % 
\def\labelenumi{\theenumi.}
\def\theenumi{\@arabic\c@enumi}
\makeatother
%% STOP IGNORING NOW

\begin{document}

\title{Positivity preservers forbidden to operate on diagonal blocks}
\author{Prateek Kumar Vishwakarma} %Presenting author only
\address{University of Regina, Canada} % Affiliation of presenting author
\email{pvg454@uregina.ca, prateekv@iisc.ac.in} % Email address of presenting author only

\maketitle

The question of which functions acting entrywise preserve positive semidefiniteness has a long history, beginning with the Schur product theorem \cite{Schur}, which implies that absolutely monotonic functions (i.e., power series with nonnegative coefficients) preserve positivity on matrices of all dimensions. A famous result of Schoenberg and of Rudin \cite{Schoenberg, Rudin} shows the converse: there are no other such functions.

Motivated by modern applications, Guillot and Rajaratnam \cite{Guillot-Rajaratnam-Trans} classified the entrywise positivity preservers in all dimensions, which act only on the off-diagonal entries. These two results are at ``opposite ends'', and in both cases the preservers have to be absolutely monotonic.

We complete in \cite{V} the classification of positivity preservers that act entrywise except on specified ``diagonal/principal blocks'', in every case other than the two above. (In fact we achieve this in a more general framework.) This yields the first examples of dimension-free entrywise positivity preservers - with certain forbidden principal blocks - that are not absolutely monotonic.

\begin{thebibliography}{1}

\bibitem{Guillot-Rajaratnam-Trans}
Dominique Guillot and Bala Rajaratnam.
\newblock Functions preserving positive definiteness for sparse matrices.
\newblock {\em Trans. Amer. Math. Soc.}, 367(1):627--649, 2015.

\bibitem{Rudin}
Walter Rudin.
\newblock Positive definite sequences and absolutely monotonic functions.
\newblock {\em Duke Math. J.}, 26:617--622, 1959.

\bibitem{Schoenberg}
Isaac~J. Schoenberg.
\newblock Positive definite functions on spheres.
\newblock {\em Duke Math. J.}, 9:96--108, 1942.

\bibitem{Schur}
Issai Schur.
\newblock Bemerkungen zur {T}heorie der beschr\"{a}nkten {B}ilinearformen mit
  unendlich vielen {V}er\"{a}nderlichen.
\newblock {\em J. Reine Angew. Math.}, 140:1--28, 1911.

\bibitem{V}
Prateek Kumar Vishwakarma.
\newblock Positivity preservers forbidden to operate on diagonal blocks.
\newblock {\em Trans. Amer. Math. Soc.}, \href{https://doi.org/10.1090/tran/8256}{https://doi.org/10.1090/tran/8256}. [\href{https://arxiv.org/abs/2002.00332v4}{arXiv}]

\end{thebibliography}
\end{document}