% Template for post or presentation abstracts submitted to ILAS 2022
% 1. Fill in the presenter's information (name, affiliation, email
% address) and talk information (title of presentation, abstract).
% 2. Compile to make sure there are no errors.
% 3. Save the .tex file for your abstract with a distinctive name,
% ideally "FamilynameGivenname.tex".
% 4. Upload your .tex file to https://clr.ie/129557
%       
% * Please keep your LaTeX commands simple, and avoid the use of
%    user-defined macros.
% * Include details of co-authors and funding acknowledgements after the abstract.
% * Upload only the LaTeX file (with .tex extension).
% * Questions: Contact Niall Madden (Niall.Madden@NUIGalway.ie)

\documentclass[a4paper]{amsart} 
\usepackage{amssymb} 
\usepackage{hyperref}
\pagestyle{empty}
\date{} 

%% IGNORE THE NEXT 4 LINES
\makeatletter % 
\def\labelenumi{\theenumi.}
\def\theenumi{\@arabic\c@enumi}
\makeatother
%% STOP IGNORING NOW

\begin{document}

\title{Distance ideals of graphs}
\author{Carlos A. Alfaro} %Presenting author only
\address{Banco de M\'exico} % Affiliation of presenting author
\email{alfaromontufar@gmail.com} % Email address of presenting author only

\maketitle

% The abstract  ***no more than one page***

Distance ideals of graphs generalize, among other graph paramethers, the spectrum and the Smith normal form (SNF) of distance and distance Laplacian matrices.
In particular, they allow us to introduce the notion of codeterminantal graphs, which generalize the concepts of cospectral and coinvariant graphs. We show computational results on codeterminantal graphs up to 9 vertices.
Although the spectrum of several graph matrices has been widely used to determine graphs, the computational results suggest that the SNF of the distance Laplacian matrix seems to perform better for determining graphs. 
Finally, we show that complete graphs and star graphs are determined by the SNF of its distance Laplacian matrix.


\emph{This is joint work with Aida Abiad (Eindhoven University of Technology and Ghent University), Kristin Heysse (Macalester College), Libby Taylor (Stanford University) and Marcos C. Vargas (Banco de M\'exico).
%This talk was part of the invited Mini-Symposium talks on Distance matrices of graphs at ILAS 2020. 
%Supported by the Sistema Nacional de Investigadores and Consejo Nacional de Ciencia y Tecnolog\'ia.
}

\begin{thebibliography}{1}

\bibitem{AA}
Aida Abiad and Carlos A. Alfaro.
\newblock Enumeration of cospectral and coinvariant graphs.
\newblock {\em Appl. Math. Comput.} 58:305--313, (2019).

\bibitem{AAHV}
Aida Abiad, Carlos A. Alfaro, Kristin Heysse and Marcos C. Vargas.
\newblock Eigenvalues, Smith normal form and determinantal ideals.
\newblock Preprint arXiv:1910.12502.

\bibitem{AT}
Carlos A. Alfaro and Libby Taylor.
\newblock Distance ideals of graphs.
\newblock {\em  Linear Algebra Appl.}  584:127--144, (2020).

\end{thebibliography}


\end{document}


% Please leave the next bit alone  
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ILAS-2022"
%%% End: