% Template for post or presentation abstracts submitted to ILAS 2022
% 1. Fill in the presenter's information (name, affiliation, email
% address) and talk information (title of presentation, abstract).
% 2. Compile to make sure there are no errors.
% 3. Save the .tex file for your abstract with a distinctive name,
% ideally "FamilynameGivenname.tex".
% 4. Upload your .tex file to https://clr.ie/129557
%       
% * Please keep your LaTeX commands simple, and avoid the use of
%    user-defined macros.
% * Include details of co-authors and funding acknowledgements after the abstract.
% * Upload only the LaTeX file (with .tex extension).
% * Questions: Contact Niall Madden (Niall.Madden@NUIGalway.ie)

\documentclass[a4paper]{amsart} 
\usepackage{amssymb} 
\usepackage{hyperref}
\pagestyle{empty}
\date{} 

%% IGNORE THE NEXT 4 LINES
\makeatletter % 
\def\labelenumi{\theenumi.}
\def\theenumi{\@arabic\c@enumi}
\makeatother
%% STOP IGNORING NOW

\begin{document}

\title{Distance-preserving bijections between sets of invertible elements in unital Jordan-Banach algebras}
\author[A.M. Peralta]{Antonio M. Peralta} %Presenting author only
\address{Instituto de Matemáticas de la Universidad de Granada (IMAG). Departamento de An{\'a}lisis Matem{\'a}tico, Facultad de	Ciencias, Universidad de Granada, 18071 Granada, Spain.}
\email{aperalta@ugr.es} % Email address of presenting author only

\maketitle

% The abstract  ***no more than one page***

It is known that the structure of the group, $A^{-1},$ of invertible elements of a unital Banach algebra $A$ does not determine uniquely the structure of the algebra, there are examples of non-isomorphic unital Banach 
algebras $A$ and $B$ whose groups of invertible elements are topologically isomorphic. If we also assume a preservation of the metric structure induce by the norm on the group of invertible elements, the answer is different. O. Hatori proved in \cite{Hat09} that, for each surjective isometry $\Delta$ from an open subgroup of the group of invertible elements in an associative unital semisimple commutative Banach algebra $A$ onto an open subgroup of the group of invertible elements in an associative unital Banach algebra $B$, the mapping $\Delta(\textbf{1})^{-1} \Delta$ is an isometric group isomorphism, which extends to an isometric real-linear algebra isomorphism from $A$ onto $B$.\smallskip

In this talk we shall try to understand the general form of a bijection preserving distances between the sets,  $M^{-1}$ and $N^{-1}$, of invertible elements of two unital Jordan-Banach algebras $M$ and $N,$ respectively. In this case, if  $\mathfrak{M}\subseteq M^{-1}$ and $\mathfrak{N}\subseteq N^{-1}$ are clopen subsets of $M^{-1}$ and $N^{-1}$, respectively, which are closed for powers, inverses and products of the form $U_{a} (b)$, and $\Delta : \mathfrak{M}\to \mathfrak{N}$ is a surjective isometry, then there exists a surjective real-linear isometry $T_0: M\to N$ and an element $u_0$ in the McCrimmon radical of $N$ such that $\Delta (a) = T_0(a) +u_0$ for all $a\in \mathfrak{M}$. The conclusion is even more satisfactory in the case of unital JB$^*$-algebras.\smallskip

%This is a sample abstract for talks and posters
%presented at ILAS 2022, to be held
%in Galway (Ireland) in June 2022. 
%
%Please, follow the instructions at \url{http://ilas2022.ie/abstracts/}
%for submitting your abstract. Make sure you upload the \texttt{.tex}
%file, and not any others. 
%
%Try to keep your file as simple as possible, so that it is easily
%rendered in various formats. Give the file a name that readily
%identifies it with you, for example \texttt{OlgaTaussky.tex}. 
%
%If you wish to include citations, you can do so like this:
%\cite{my_key_for_OT49}. Use a bibitem key that is likely be be unique to
%you (e.g., don't use the default Math Reviews key).
%Any uncited bibliography entries will also
%appear. If you have none, then delete that section.
%
%%% Coauthor details here (optional - delete if not applicable)
%% and funding acknowledgment (optional - delete if not applicable)
%\emph{This is joint work with John Todd (Caltech) and Alexander Ostrowski (Basel).
%Supported by the National Mathematics Foundation, Grant XYZ-123.}

\begin{thebibliography}{1}
\bibitem{Hat09} O. Hatori.  
\newblock Isometries between groups of invertible elements in Banach algebras. 
\newblock \emph{Studia Math.} {194}:293--304, 2009.

\bibitem{Pe21} A.M. Peralta. 
\newblock Surjective isometries between sets of invertible elements in unital Jordan-Banach algebras. 
\newblock \emph{J. Math. Anal. Appl.} 502, no. 2, Paper No. 125284, 2021.

%\bibitem{my_key_for_OT49}
%Olga Taussky.
%\newblock A recurring theorem on determinants.
%\newblock {\em  Amer. Math. Monthly}  56:672–676,  (1949).

%\bibitem{another_unique_key}
%Olga Taussky and John Todd.
%\newblock Cholesky, Toeplitz and the triangular factorization of
%symmetric matrices.
%\newblock {\em  Numer. Algorithms}, 41(2):197--202, 2006.
\end{thebibliography}


\end{document}


% Please leave the next bit alone  
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ILAS-2022"
%%% End:
