% Exercises-1-HW
% 1920-MA385 Homework assignment 1
% Author: Niall Madden  Niall.Madden@NUIGalway.ie
\documentclass[a4paper, notitlepage,12pt]{report}

\usepackage{amsmath,amsthm, amssymb}
%\usepackage{xr}
%\externaldocument{1-NonlinearEquatons}

\usepackage{fancyhdr}
\usepackage[body={17.5cm,25.2cm},centering,  nofoot]{geometry}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{eulervm}

\renewcommand{\familydefault}{\sfdefault} 


\newcommand {\Rsym}{{ \mathbb{R}^{n \times n}_\mathrm{sym}}}

\newtheorem{exercise}{Exercise}[chapter]

\linespread{1.2}

\newcounter{tmp}
\newcommand{\saveexer}{\setcounter{tmp}{\theexercise}}
\newcommand{\loadexer}{\setcounter{exercise}{\thetmp}}

\author{Niall Madden}
\title{1920-MA385 -- Numerical Analysis I (``NA1'')}

\newcommand{\ChapterTitle}{ ~ }
\newcommand{\SectionTitle}{ ~ }
\pagestyle{fancy}
\renewcommand{\sectionmark}[1]{\markright{%Lecture \thesection\
    \boldmath\textbf{\SectionTitle}\unboldmath}}
\renewcommand{\subsectionmark}[1]{%
\markright{%Lecture \thesection\ 
\boldmath\textbf{\SectionTitle}\unboldmath}}

\fancyhf{}   
\fancyhead[C]{\textbf{\thepage}}      %
\fancyhead[R]{}
\fancyhead[L]{\S 1920--MA385 Chapter 0 and 1: Exercises}
\renewcommand{\headrulewidth}{1pt}      %Underlines the header. (Set to 0pt if not required).

\begin{document}

\renewcommand{\ChapterTitle}{Solving nonlinear equations}
\setcounter{chapter}{0}
%\twocolumn[
\begin{center}
{\Large Chapter 0 (Taylor's Theorem) and Chapter 1 (\ChapterTitle)}

\emph{\large Please submit carefully written solutions to the
  following exercises: \\
  Exercises
  \ref{exer:Taylor sin}
  \ref{exer:derive Newton},
  \ref{exer:newton converge},
  \ref{exer:Newton error formula},
  and
  \ref{exer:g contracts?}.
}

\end{center}


\setcounter{chapter}{0}
\setcounter{exercise}{1}
% \input{Exercises-0-1}
\begin{exercise}[$\star$  Homework problem]
  \label{exer:Taylor sin}
  Write out the Taylor polynomial at  $x$, about $a=0$, of degree 5 for
  $f(x)=\sin(x)$. How does its derivative compare to the corresponding
  Taylor polynomial for $f(x)=\cos(x)$?
\end{exercise}

\setcounter{chapter}{1}
\setcounter{exercise}{0}
\setcounter{exercise}{7}
\begin{exercise}[$\star$ Homework problem] 
  \label{exer:derive Newton} 
Write down the equation of the line that is tangential to the
  function $f$ at the point $x_k$. Give an expression for its
  zero. Hence show how to derive Newton's method.
\end{exercise}

\setcounter{exercise}{9}
\begin{exercise}[$\star$ Homework problem]
  \label{exer:newton converge}
  \begin{enumerate}[(i)]
  \item Let $q$ be your student ID number.
    Find $k$ and $m$ where $k-2$ is the remainder on dividing $q$ by 4,
    and $m-2$ is the remainder on dividing $q$ by 6.
    
  \item Show how Newton's method can be applied to estimate the
    postive real number $\displaystyle \sqrt[k]{m}$.
    That is, state the nonlinear equation you would solve, and give
    the formula for Newton's method, simplified as much as  possible.
    
\item Do three iterations by hand of Newton's Method for this problem.
\end{enumerate}
\end{exercise}

\begin{exercise}[$\star$  Homework problem] 
  \label{exer:Newton error formula}
  Suppose we want to apply Newton's method to solving $f(x)=0$ where $f$
  is such that  ${|f''(x)|\leq 10}$ and $|f'(x)| \geq 2$ for all
  $x$.
  How close must $x_0$ be to $\tau$ for the method to converge?
\end{exercise}

\setcounter{exercise}{14}
\begin{exercise}[$\star$ Homework problem] 
\label{exer:g contracts?}
 Show that $g(x) = \ln(2x +1)$ is a contraction on $[1,2]$. Give
an estimate for $L$. (Hint: Use the Mean Value Theorem).
\end{exercise}

\end{document}

\end{document}
