% Template for post or presentation abstracts submitted to ILAS 2022
% 1. Fill in the presenter's information (name, affiliation, email
% address) and talk information (title of presentation, abstract).
% 2. Compile to make sure there are no errors.
% 3. Save the .tex file for your abstract with a distinctive name,
% ideally "FamilynameGivenname.tex".
% 4. Upload your .tex file to https://clr.ie/129557
%       
% * Please keep your LaTeX commands simple, and avoid the use of
%    user-defined macros.
% * Include details of co-authors and funding acknowledgements after the abstract.
% * Upload only the LaTeX file (with .tex extension).
% * Questions: Contact Niall Madden (Niall.Madden@NUIGalway.ie)

\documentclass[a4paper]{amsart} 
\usepackage{amssymb} 
\usepackage{hyperref}
\pagestyle{empty}
\date{} 

%% IGNORE THE NEXT 4 LINES
\makeatletter % 
\def\labelenumi{\theenumi.}
\def\theenumi{\@arabic\c@enumi}
\makeatother
%% STOP IGNORING NOW

\begin{document}

\title{Tropical Matrix Identities}
\author{Adi Niv} %Presenting author only
\address{Kibbutzim College} % Affiliation of presenting author
\email{adi.niv@smkb.ac.il} % Email address of presenting author only

\maketitle

% The abstract  ***no more than one page***

Tropical matrix theory is well known for its combinatorial nature. Applying the equivalency between graph theory and matrix theory, over the Max-Plus semiring, Butkovic showed~\cite{But03} that the tropical setting gives interpretations to known combinatorial problems. We prove identities on compound matrices in extended tropical semirings. Such identities include analogues to properties of conjugate matrices, powers of matrices and Sylvester-Franke identity, all of which are of strong combinatorial flavor. 

\ 

We then provide a new graph theoretic proof of the tropical Jacobi identity, connecting the compound of the inverse to the inverse of the compound. Following Butkovic's interpretations to tropical matrix identities, we develop an application of this theorem to optimal assignments with supervisions. That is, optimally assigning multiple tasks to one team, or daily tasks to multiple teams, where each team has a supervisor task or a supervised task.




%% Coauthor details here (optional - delete if not applicable)
% and funding acknowledgment (optional - delete if not applicable)
\emph{This is joint work with S. Gaubert, M. Akian, S. Sergeev and M. MacCaig}

\begin{thebibliography}{1}
\bibitem{But03}
P. Butkovic
\newblock Max-algebra: the linear algebra of combinatorics? 
\newblock {\em  Linear Algebra Appl.,} 367:313–335, 2003.


\end{thebibliography}


\end{document}


% Please leave the next bit alone  
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ILAS-2022"
%%% End:
