% Template for post or presentation abstracts submitted to ILAS 2022
% 1. Fill in the presenter's information (name, affiliation, email
% address) and talk information (title of presentation, abstract).
% 2. Compile to make sure there are no errors.
% 3. Save the .tex file for your abstract with a distinctive name,
% ideally "FamilynameGivenname.tex".
% 4. Upload your .tex file to https://clr.ie/129557
% * Please keep your LaTeX commands simple, and avoid the use of
%    user-defined macros.
% * Include details of co-authors and funding acknowledgements after the abstract.
% * Upload only the LaTeX file (with .tex extension).
% * Questions: Contact Niall Madden (Niall.Madden@NUIGalway.ie)
%% IGNORE THE NEXT 4 LINES
%% STOP IGNORING NOW


\documentclass[a4paper]{amsart}
\usepackage{eurosym}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amssymb}
\usepackage{hyperref}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2953}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%TCIDATA{LastRevised=Wednesday, March 16, 2022 17:23:23}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}

\pagestyle{empty}
\makeatletter 
\def\labelenumi{\theenumi.}
\def\theenumi{\@arabic\c@enumi}
\makeatother

\input{tcilatex}

\begin{document}
\date{}
\title{Efficient vectors for perturbed consistent matrices}
\author{Susana Furtado}
\address{CEAFEL and Faculdade de Economia do Porto}
\email{sbf@fep.up.pt}
\maketitle

%Presenting author only

% Affiliation of presenting author

% Email address of presenting author only

% The abstract  ***no more than one page***

An $n\times n$ matrix $A=[a_{ij}]$ is said to be a pairwise comparison
matrix (PC matrix) or a reciprocal matrix if it is positive and $a_{ij}=%
\frac{1}{a_{ji}},$ for $i,j=1,\ldots ,n.$ If, in addition, $%
a_{ij}a_{jk}=a_{ik,}$ for $i,j,k=1,\ldots ,n,$ then $A$ is said to be
consistent or transitive.

PC matrices and, in particular, consistent matrices, play an important role
in the Analytic Hierarchy Process, a method used in Decision Making. In this
method it may be important to approximate a PC matrix by a consistent one.
In this context, the notion of efficient vector for a PC matrix arises.

A positive vector $w=\left[ 
\begin{array}{ccc}
w_{1} & \cdots  & w_{n}%
\end{array}%
\right] ^{T}$ is said to be efficient for an $n\times n$ PC matrix $%
A=[a_{ij}]$ if there is no other vector $v=\left[ 
\begin{array}{ccc}
v_{1} & \cdots  & v_{n}%
\end{array}%
\right] ^{T}$ such that 
\[
\left\vert a_{ij}-\frac{v_{i}}{v_{j}}\right\vert \leq \left\vert a_{ij}-%
\frac{w_{i}}{w_{j}}\right\vert \text{ \qquad for all }1\leq i,j\leq n,
\]%
with the inequality strict for at least one pair $(i,j).$ 

In this talk we describe all efficient vectors for a simple perturbed
consistent matrix, that is, a PC matrix obtained from a consistent one by
perturbing one entry above the main diagonal, and the corresponding
reciprocal entry. As a consequence, we give a simple proof of the result
obtained by K. \'{A}bele-Nagy and S. Boz\'{o}ki (2016) that states that any
(positive) eigenvector of a simple perturbed consistent matrix associated
with the Perron eigenvalue is efficient. Some related results for double and
triple perturbed consistent matrices are also presented.


%% Coauthor details here (optional - delete if not applicable)
% and funding acknowledgment (optional - delete if not applicable)
\emph{Based on a joint work with Henrique Cruz and Ros\'{a}rio Fernandes.}

\end{document}
